6.867 Problem Set 2

### 2015-10-26 HW2/tex/HW2.tex

@@

>>>>

\begin{table}
\captionof{table}{Soft SVM Performance for Different Parameters and Kernels} 
\centering
\begin{tabular}{llllll}
\toprule
{} &                        Kernel &      $C$ &   $\sigma$ &    Number of Support Vectors & $1/||\mathbf{w}||$ \\
\midrule
&    Gaussian &    .01 &    .1 &   400 &    .0286 \\
&    Gaussian &    .01 &    1 &   400 &    .0286 \\
&    Gaussian &    .01 &    10 &   400 &    .0286 \\
&    Gaussian &    .1 &    .1 &   400 &    .0141 \\
&    Gaussian &    .1 &    1 &   400 &    .0207 \\
&    Gaussian &    .1 &    10 &   400 &    .0141 \\
&    Gaussian &    1 &    .1 &   391 &    .0022 \\
&    Gaussian &    1 &    1 &   100 &    .0076 \\
&    Gaussian &    1 &    10 &   368 &    .0018 \\
&    Gaussian &    10 &    .1 &   390 &    .0018 \\
&    Gaussian &    10 &    1 &   71 &    .0017 \\
&    Gaussian &    10 &    10 &   209 &    .0003 \\
&    Gaussian &    100 &    .1 &   390 &    .0018 \\
&    Gaussian &    100 &    1 &   59 &    .0002 \\
&    Gaussian &    100 &    10 &   159 &    7.51e-5 \\
&    Linear &    .01 &    N/A &   399 &    .0282 \\
&    Linear &    .1 &    N/A &   393 &    .0133 \\
&    Linear &    1 &    N/A &   392 &    .0017 \\
&    Linear &    10 &    N/A &   393 &    .0002 \\
&    Linear &    100 &    N/A &   397 &    1.8e-5 \\
\midrule
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[height=3in]{titanic_weight_comparison.png}
	\caption*{Comparison of Feature Weights Across Models (Normalized per Model)}
\end{figure}
